Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation

### 2015-04-07 experiments.tex
extended abstract and Michael's edit

\paragraph{Results.}
In Tab.~\ref{tab:who_initializations}, we observe that, on average,
calibration indeed improves performance in terms of AP, sometimes
drastically (e.g., from $54.4$ to $92.8$ for WHO-CG-Z), as observed in
prior work~\cite{Aubry14}. At the same time, calibration is
computationally expensive, resulting in generation time that are two orders of
magnitudes larger than without calibration. Strikingly, our method
NZ-WHO-CG achieves the second best AP of $90.0$ while completing in 79
ms vs. 8.7 s when using calibration.

@@

\begin{table}[!htbp]
  \footnotesize
  \setlength{\tabcolsep}{1pt}
  \centering
  \begin{tabular}{|c|c|r|c|r|}
    \hline
    Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
    \hline\hline
    HOG\cite{Dalal05}      & 72.3 / 65.0          &  31ms  & 60.4 / 50.2           & 8.7 sec \\ 
    WHO\cite{Hariharan12}  & 82.1 / \textbf{85.4} &  6162ms& 84.4 / 83.0           & 15.4 sec\\
    WHO-CG                 & 81.7 / 84.9          &  104ms & 83.7 / \textbf{87.3}  & 8.3 sec \\
    WHO-CG-Z               & 54.4 / 65.1          &  103ms & \textbf{92.8} / 86.7  & 8.7 sec \\
    % NZC-WHO-Z    & 89.10 /\textbf{78.64} &    & 91.15 / 74.79                  &     \\
    NZ-WHO-CG {\em (ours)} & \textbf{90.0} / 82.8 &   79ms & 90.3 / 86.8           & 8.5 sec \\
    \hline
  \end{tabular}
  \caption{Average Precision(AP), Mean Precision in Pose Estimation
    (MPPE)~\cite{Lopez-Sastre11}, and generation time for variations of WHO on
    3D Object Classes cars~\cite{Savarese07}. Please see text for
    details.}
  % WHO refers to standard WHO using the
  % method presented in \cite{Hariharan12}, WHO-CG uses iterative
  % Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the
  % whole template and zero out textureless region. NZ-WHO-CG is the
  % NZ-WHO which whitens only non-zero cells using iterative Conjugate
  % Gradient method. The time column indicates the time to generate one
  % template. We followed calibration procedure presented in \cite{Aubry14}.}
  \label{tab:who_initializations}
\end{table}

@@

This result is encouraging, since our approach reaches a level of
performance that is on par to current state-of-the-art while at the
same time being much faster to train. It takes merely a few minutes to
train, while both ALM~\cite{Xiang12} and DPM-VOC+VP~\cite{Pepik12} are
complex models that optimize non-convex objective functions during
training, which is only made tractable by resorting to delayed
constraint generation in the form of hard negative mining, and can
easily take a day on a single machine. In addition, our approach uses
only rendered images, avoiding the need for real-world training data
with costly bounding box and viewpoint annotations.
%
\begin{table}[!htbp]
    \footnotesize
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
     AP/MPPE& Ours & ALM\cite{Xiang12} & VOC-DPM\cite{Pepik12} \\
    \hline\hline
    car     & \textbf{99.8} / 91.7 & 98.4 / 93.4 & \textbf{99.8} / \textbf{97.5} \\ 
    bicycle & 93.0 / 90.9          & 93.0 / 91.4 & \textbf{98.8} / \textbf{97.5} \\
    \hline
    \end{tabular}
  \end{center}
  \caption{Average Precision (AP) and Mean Precision in Pose
    Estimation (MPPE) on 3D Object Classes~\cite{Savarese07} cars.}% Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
  \label{tab:3dobject}
\end{table}

@@

To show such ability, we evaluate our method on the PASCAL3D+
dataset~\cite{Xiang14}. This dataset augments PASCAL 2012 images with
high quality viewpoint annotations thus is ideal to measure pose
estimation. The dataset proposes new metric called Average Viewpoint
Precision (AVP) where it measures the area under viewpoint precision
and detection recall curve. The viewpoints is measured by azimuth
similarity. If the distance between predicted azimuth and ground truth
azimuth is below a certain threshold, the viewpoint is correct.
The baseline methods V-DPM~\cite{Xiang14} and
DPM-VOC+VP~\cite{Pepik12}) reported on the PASCAL3D+ dataset are
variants of DPM~\cite{Felzenszwalb10} where each component of DPM
account for various azimuths. Thus V-DPM and VOC-DPM provide discrete
azimuths only whereas our method provides 3D viewpoint (yaw, pitch,
roll), CAD instance (model index, rendering, depth) and focal length.
%
\begin{figure}[t]
 \begin{center}
    \setlength\tabcolsep{0pt}
    \begin{tabular}{ccc}
    % \includegraphics[width=0.9\linewidth]{tuning} 
   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
%   (a) & (b) & (c)\\
   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
%   (d) & (e) & (f)\\
   \end{tabular}
 \end{center}
 \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning using Single-Component Metropolis Hastings}
 \label{fig:tuning}
\end{figure}

\paragraph{Setup.}
We use detection bounding boxes provided by both object detectors and
augment use our method to perform fine-grained viewpoint estimation. We use
detection bounding boxes from two different methods:
DPM-VOC+VP\cite{Pepik12} and R-CNN~\cite{Girshick14}, both in their
variants trained on 8 viewpoint categories, since these perform best
in terms of AP. For both cases,
we use the original score for plotting precision-recall curves
(meaning that we can not improve over their AP). We revert back to a default
viewpoint prediction ($0$ angles) in case the confidence of our
method falls below a threshold.

@@

%  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
%  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
%  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
%  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  

@@

  reasonably. The first column shows bounding boxed produced by R-CNN detection. Subsequent columns show the output of our method given this bounding box input. Blue boxes are R-CNN output and purple boxes are

@@

    aeroplane-4v        & 40.0 / 34.6         & 41.5 / 37.4             & 41.1 / 32.7       & 41.1 / 30.5        & 67.8 / \textbf{41.3}         & 67.8 / 40.8 \\ \hline
    aeroplane-8v        & 39.8 / 23.4         & 40.5 / 28.6             & 41.1 / 26.8       & 41.1 / 24.2        & 67.8 / 26.8         & 67.8 / \textbf{27.4} \\ \hline
    aeroplane-16v       & 43.6 / 15.4         & 38.0 / 15.9             & 41.1 / 17.7       & 41.1 / 16.3        & 67.8 / 21.2         & 67.8 / \textbf{21.5} \\ \hline
    aeroplane-24v       & 42.2 / 8.0          & 36.0 /  9.7             & 41.1 / 10.9       & 41.1 / 10.2        & 67.8 / 15.6         & 67.8 / \textbf{15.7} \\ \hline

@@

    chair-4v            & 11.1 / 6.8          & 8.7  / 6.1              &  11.4 / 7.1       & 11.4 / 6.7         & 25.2 / 10.6         & 25.2 / \textbf{10.7} \\ \hline
    chair-8v            & 11.4 / 5.9          & 11.3 / 9.4              &  11.4 / 6.6       & 11.4 / 6.6         & 25.2 / \textbf{9.4}          & 25.2 / 9.3 \\ \hline
    chair-16v           & 12.8 / 6.0          & 10.2 / 6.1              &  11.4 / 4.7       & 11.4 / 4.7         & 25.2 / \textbf{6.7}          & 25.2 / 6.7 \\ \hline
    chair-24v           & 12.6 / 4.4          & 8.0  / 4.2              &  11.4 / 3.1       & 11.4 / 3.4         & 25.2 / 4.6          & 25.2 / \textbf{5.4} \\ \hline

>>>>

\paragraph{Results.}
In Tab.~\ref{tab:who_initializations}, we observe that, on average,
calibration indeed improves performance in terms of AP, sometimes
drastically (e.g., from $54.4$ to $92.8$ for WHO-CG-Z), as observed in
prior work~\cite{Aubry14}. At the same time, calibration is
computationally expensive, resulting in generation time that are two orders of
magnitudes larger than without calibration. Strikingly, our method
NZ-WHO-CG achieves the second best AP of $90.0$ while completing in 79
ms vs. 8.5 s when using calibration.

@@

\begin{table}[!htbp]
  \footnotesize
  \setlength{\tabcolsep}{1pt}
  \centering
  \begin{tabular}{|c|c|r|c|r|}
    \hline
    Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
    \hline\hline
    HOG\cite{Dalal05}      & 72.3 / 65.0          &  31ms  & 60.4 / 50.2           & 8.7 sec \\ 
    WHO\cite{Hariharan12}  & 82.1 / \textbf{85.4} &  6162ms& 84.4 / 83.0           & 15.4 sec\\
    WHO-CG                 & 81.7 / 84.9          &  104ms & 83.7 / \textbf{87.3}  & 8.3 sec \\
    WHO-CG-Z               & 54.4 / 65.1          &  103ms & \textbf{92.8} / 86.7  & 8.7 sec \\
    % NZC-WHO-Z    & 89.10 /\textbf{78.64} &    & 91.15 / 74.79                  &     \\
    NZ-WHO-CG {\em (ours)} & \textbf{90.0} / 82.8 &   79ms & 90.3 / 86.8           & 8.5 sec \\
    \hline
  \end{tabular}
  \caption{Average Precision (AP), Mean Precision in Pose Estimation
    (MPPE)~\cite{Lopez-Sastre11}, and generation time for variations of WHO on
    3D Object Classes cars~\cite{Savarese07}. Please see text for
    details.}
  % WHO refers to standard WHO using the
  % method presented in \cite{Hariharan12}, WHO-CG uses iterative
  % Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the
  % whole template and zero out textureless region. NZ-WHO-CG is the
  % NZ-WHO which whitens only non-zero cells using iterative Conjugate
  % Gradient method. The time column indicates the time to generate one
  % template. We followed calibration procedure presented in \cite{Aubry14}.}
  \label{tab:who_initializations}
\end{table}

@@

This result is encouraging, since our approach reaches a level of
performance that is on par to current state-of-the-art while at the
same time being much faster to train. It takes merely a few minutes to
train, while both ALM~\cite{Xiang12} and DPM-VOC+VP~\cite{Pepik12} are
complex models that optimize non-convex objective functions during
training, which is only made tractable by resorting to delayed
constraint generation in the form of hard negative mining, and can
easily take a day on a single machine. In addition, our approach uses
only rendered images, avoiding the need for real-world training data
with costly bounding box and viewpoint annotations.
%
\begin{table}[!htbp]
    \footnotesize
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
    AP/MPPE& Ours & ALM\cite{Xiang12} & DPM-VOC+VP\cite{Pepik12} \\
    \hline\hline
    car     & \textbf{99.8} / 91.7 & 98.4 / 93.4 & \textbf{99.8} / \textbf{97.5} \\ 
    bicycle & 93.0 / 90.9          & 93.0 / 91.4 & \textbf{98.8} / \textbf{97.5} \\
    \hline
    \end{tabular}
  \end{center}
  \caption{Average Precision (AP) and Mean Precision in Pose
    Estimation (MPPE) on 3D Object Classes~\cite{Savarese07} cars.}% Our method produces high quality 2D-3D matching yet performs on par with state-of-the art detectors.}
  \label{tab:3dobject}
\end{table}

@@

To show such ability, we evaluate our method on the PASCAL3D+
dataset~\cite{Xiang14}. This dataset augments PASCAL 2012 images with
high quality viewpoint annotations thus is ideal to measure pose
estimation. The dataset proposes a new metric called Average Viewpoint
Precision (AVP) where it measures the area under viewpoint precision
and detection recall curve. The viewpoint is measured by azimuth
similarity. If the distance between predicted azimuth and ground truth
azimuth is below a certain threshold, the viewpoint is correct.
The baseline methods V-DPM~\cite{Xiang14} and
DPM-VOC+VP~\cite{Pepik12} reported on the PASCAL3D+ dataset are
variants of DPM~\cite{Felzenszwalb10} where each component of DPM
accounts for azimuth. Thus V-DPM and DPM-VOC+VP provide discrete
azimuths only whereas our method provides 3D viewpoint (yaw, pitch,
roll), CAD model instance (model index, rendering, depth) and focal length.
%
\begin{figure}[t]
 \begin{center}
    \setlength\tabcolsep{0pt}
    \begin{tabular}{ccc}
    % \includegraphics[width=0.9\linewidth]{tuning} 
   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
%   (a) & (b) & (c)\\
   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
%   (d) & (e) & (f)\\
   \end{tabular}
 \end{center}
 \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning using Single-Component Metropolis Hastings}
 \label{fig:tuning}
\end{figure}

\paragraph{Setup.}
We use detection bounding boxes provided by both object detectors and
 use our method to perform fine-grained viewpoint estimation. We use
detection bounding boxes from two different methods:
DPM-VOC+VP~\cite{Pepik12} and R-CNN~\cite{Girshick14}, both in their
variants trained on 8 viewpoint categories, since these perform best
in terms of AP. For both cases,
we use the original score for plotting precision-recall curves
(meaning that we can not improve over their AP). We revert back to a default
viewpoint prediction ($0$ angles) in case the confidence of our
method falls below a threshold.

@@

  \includegraphics[width=0.24\textwidth]{car_cnn/2a.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2b.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2c.png} &   
  \includegraphics[width=0.24\textwidth]{car_cnn/2e.png}  \\  

@@

  reasonably. The first column shows bounding boxes produced by R-CNN detection. Subsequent columns show the output of our method given this bounding box input. Blue boxes are R-CNN output and purple boxes are

@@

%    aeroplane-4v        & 40.0 / 34.6         & 41.5 / 37.4             & 41.1 / 32.7       & 41.1 / 30.5        & 67.8 / \textbf{41.3}         & 67.8 / 40.8 \\ \hline
%    aeroplane-8v        & 39.8 / 23.4         & 40.5 / 28.6             & 41.1 / 26.8       & 41.1 / 24.2        & 67.8 / 26.8         & 67.8 / \textbf{27.4} \\ \hline
%    aeroplane-16v       & 43.6 / 15.4         & 38.0 / 15.9             & 41.1 / 17.7       & 41.1 / 16.3        & 67.8 / 21.2         & 67.8 / \textbf{21.5} \\ \hline
%    aeroplane-24v       & 42.2 / 8.0          & 36.0 /  9.7             & 41.1 / 10.9       & 41.1 / 10.2        & 67.8 / 15.6         & 67.8 / \textbf{15.7} \\ \hline

@@

%    chair-4v            & 11.1 / 6.8          & 8.7  / 6.1              &  11.4 / 7.1       & 11.4 / 6.7         & 25.2 / 10.6         & 25.2 / \textbf{10.7} \\ \hline
%    chair-8v            & 11.4 / 5.9          & 11.3 / 9.4              &  11.4 / 6.6       & 11.4 / 6.6         & 25.2 / \textbf{9.4}          & 25.2 / 9.3 \\ \hline
%    chair-16v           & 12.8 / 6.0          & 10.2 / 6.1              &  11.4 / 4.7       & 11.4 / 4.7         & 25.2 / \textbf{6.7}          & 25.2 / 6.7 \\ \hline
%    chair-24v           & 12.6 / 4.4          & 8.0  / 4.2              &  11.4 / 3.1       & 11.4 / 3.4         & 25.2 / 4.6          & 25.2 / \textbf{5.4} \\ \hline

### 2015-04-07 intro.tex
extended abstract and Michael's edit

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of WHO. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing. We call these NZ-WHO templates \ref{fig:front}. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuous pose space, consisting of yaw, pitch and roll, which
we implement using MCMC sampling.

@@

First, we present a novel method for training exemplar models from
rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
WHO, termed NZ-WHO, and making efficient use of the specific
characteristics of rendered images. To our knowledge, our method
constitutes the first attempt to simultaneously render and train
exemplar detectors on the fly.
% In our paper, we present Non-Zero Whiten Histograms of Orientations
% (NZ-WHO) to dramatically speed up the template generation and get rid
% of time consuming calibration and yet achieves performance on par with
% calibrated templates. First, we will present NZ-WHO is more
% discriminative than WHO and introduce Conjugate Gradient method to
% speed up the whitening and create a high resolution template in just
% 80 milliseconds. Also, using this fast NZ-WHO template generation, we
% present \textbf{on-the-fly} template generation to fine tune an
% initial pose estimation to continuously refine translation, viewpoints
% (yaw, roll, pitch) and focal length.
%
Second, we demonstrate that our method can enrich the output of an existing object class
detector, such as the DPM~\cite{Felzenszwalb10} or the
R-CNN~\cite{Girshick14} with additional 3D information. By applying our
method to candidate detections provided by the respective detector, we can augment the original detections with an
estimate of 3D continuous pose and a 3D CAD model exemplar.
%
Finally, we give an in-depth experimental study that demonstrates
the effectiveness of our approach on a standard benchmark for
object detection and viewpoint estimation~\cite{Xiang14}.

>>>>

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of WHO. As a
result, we can render novel views and train corresponding exemplar
models {\em on-the-fly}, without the need for offline processing. We call these Non-Zero Whitened Histograms of Orientations (NZ-WHO) templates \ref{fig:front}. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuous pose space, consisting of yaw, pitch and roll, which
we implement using MCMC sampling.

@@

First, we present a novel method for training exemplar models from
rendered 3D CAD data {\em on-the-fly}, enabled by a novel variant of
WHO, termed Non-Zero Whitened Histograms of Orientations (NZ-WHO), and making efficient use of the specific
characteristics of rendered images. To our knowledge, our method
constitutes the first attempt to simultaneously render and train
exemplar detectors on-the-fly.
% In our paper, we present Non-Zero Whitened Histograms of Orientations
% (NZ-WHO) to dramatically speed up the template generation and get rid
% of time consuming calibration and yet achieves performance on par with
% calibrated templates. First, we will present NZ-WHO is more
% discriminative than WHO and introduce Conjugate Gradient method to
% speed up the whitening and create a high resolution template in just
% 80 milliseconds. Also, using this fast NZ-WHO template generation, we
% present \textbf{on-the-fly} template generation to fine tune an
% initial pose estimation to continuously refine translation, viewpoints
% (yaw, roll, pitch) and focal length.
%
Second, we demonstrate that our method can enrich the output of an existing object class
detector, such as the DPM~\cite{Felzenszwalb10} or the
R-CNN~\cite{Girshick14} with additional 3D information. By applying our
method to candidate detections provided by the respective detector, we can augment the original detections with an
estimate of 3D continuous pose and a 3D CAD model exemplar.
%
Finally, we give an in-depth experimental study that demonstrates
the effectiveness of our approach on a standard benchmark for
object detection and viewpoint estimation~\cite{Xiang14}.

### 2015-04-07 mcmc.tex
extended abstract and Michael's edit

\paragraph{Probabilistic formulation.}
We parameterize the continuous parameter space as  $p = [v, m, f]$,
where $v$ is the 3D rotation of the CAD model, $m$ is the discrete CAD
model index, and $f$ is the focal length.

We model the probability that the object in the test image
$\mathcal{I}$ is generated by the parameters $p$ as a distribution in
the exponential family, and let
\begin{align}
    P(p) & \sim e^{ \max_{s} w(p) \ast \mathcal{T}_s(\mathcal{I})},
\end{align}
where $\max_{s} w(p) \ast T_s(\mathcal{I})$ is the maximum convolution score of
NZ-WHO template $w(p)$ with image features $T_s(\mathcal{I})$ for all scale $s$, as defined
in Sect.~\ref{sec:nzwho}.

\paragraph{Inference.}
We approximate the MAP solution for $p$ by drawing samples from the
distribution $P(p)$, using the single component Metropolis-Hastings
algorithm. Specifically, we use a variant that changes only a single
component of the parameter vector $p$ at a time, termed Single
Component Metropolis Hastings \cite{mcmc}.

This algorithm changes the current state $p$ to a new state $q$ based
on the acceptance probability
\begin{align}
    A(p \rightarrow q) & =  min\left( 1,  \frac{P(q) g(q \rightarrow p)}{P(p) g(p \rightarrow q)}\right).
\end{align}
We define $3$ different types of moves that can alter the state
(Fig.~\ref{fig:moves}), {\em (i)} changing the focal length $f$, {\em
(ii)} one of the rotational pose parameters $v_i$, and {\em (iii)} CAD model
index $m$. For (i) and (ii), we use Gaussian proposal distributions, and a uniform
distribution over model changes for (iii). We implicitly compute all possible translation and scale by convolving $w(q)$ with a HOG pyramid.
\begin{align}
    g(p \rightarrow p + v_i') & \sim \mathcal{N}(\mu = p_{v_i},\sigma = \sigma_v) \quad i \in \{1,2,3\}\\
    g(p \rightarrow p + f') & \sim \mathcal{N}(\mu = p_{f},\sigma = \sigma_f)\\
    g(p \rightarrow p + m') & \sim (1-c) \delta(p_m) + c\,\textrm{Unif}(1,M),
\end{align}
where $g$ is the proposal distribution. % and $P$ is the distribution of which we
%defined using Gaussian distribution around previous state. $A$ is the
%acceptance probability where we accept new proposal with $A(x \rightarrow x')$.
%
% One can also think of the image as an image cropped by detection
% bounding box. We synthesize covariance matrix and create NZ-WHO
% template $w(x)$ for particular viewpoint, focal length and CAD model.
% In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
% We found out that it requires good initialization to converge to
% local minima.

@@

% there are several advantages that was not possible such as
% \textbf{on-the-fly} template generation and making large number of
% templates
\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Search space that our fine-tuning stage handles (Section~\ref{sec:fine}).}
 \label{fig:moves}
\end{figure}

\paragraph{Initialization.}
Since the objective function is non-convex, we need a good initialization in order to
increase the probability that we find a solution close to the
global optima. We achieve this by first running a discrete,
pre-trained version of our algorithm (i.e., an ensemble of NZ-WHO
templates) in order to get promising candidate 2D bounding boxes and
poses to start from. We then initialize $x_0$ for each of these candidates.

>>>>

\paragraph{Probabilistic formulation.}
We parameterize the continuous parameter space as  $\theta = [v, m, f]$,
where $v$ is the 3D rotation of the CAD model, $m$ is the discrete CAD
model index, and $f$ is the focal length.

We model the probability of an object with the parameter $\theta$ in the test
image $\mathcal{I}$ as a distribution in the exponential family, and let
\begin{align}
    P(\theta| \mathcal{I}) & \sim e^{ \max_{s} w(\theta) \ast \mathcal{T}_s(\mathcal{I})},
\end{align}
where $\max_{s} w(\theta) \ast T_s(\mathcal{I})$ is the maximum convolution score of
NZ-WHO template $w(\theta)$ with image features $T_s(\mathcal{I})$ for all scale
$s$, as defined in Sect.~\ref{sec:nzwho}.

\paragraph{Inference.}
We approximate the MAP solution for $\theta$ by drawing samples from the
distribution $P(\theta | \mathcal{I})$, using the Metropolis-Hastings
algorithm. Specifically, we use a variant that changes only a single
component of the parameter vector $p$ at a time, termed Single
Component Metropolis-Hastings \cite{mcmc}.

This algorithm changes the current state $p$ to a new state $q$ based
on the acceptance probability
\begin{align}
    A(\theta \rightarrow \theta^+) & =  min\left( 1, \frac{P(\theta^+ |
            \mathcal{I}) g(\theta^+ \rightarrow \theta)}{P(\theta | \mathcal{I})
            g(\theta \rightarrow \theta^+)}\right)
\end{align}
We define $3$ different types of moves that can alter the state
(Fig.~\ref{fig:moves}), {\em (i)} changing the focal length $f$, {\em
(ii)} one of the rotational pose parameters $v_i$, and {\em (iii)} CAD model
index $m$. For (i) and (ii), we use Gaussian proposal distributions, and a
uniform distribution over model changes for (iii). We implicitly compute all
possible translation and scale by convolving $w(\theta^+)$ with a HOG pyramid.
\begin{align}
    g(\theta \rightarrow \theta(v_i^+)) & \sim
    \mathcal{N}(\theta_{v_i},\sigma_v) \quad \mbox{ for }\; i \in \{1,2,3\}\\
    g(\theta \rightarrow \theta(f^+)) & \sim \mathcal{N}(\theta_{f}, \sigma_f)\\
    g(\theta \rightarrow \theta(m^+)) & \sim (1-c) \delta(\theta_m) +
    c\,\textrm{Unif}(1,M)
\end{align}
where $g$ is the proposal distribution, and $m \in \{1,\cdots,M\}$. 
% and $P$ is the distribution of which we
%defined using Gaussian distribution around previous state. $A$ is the
%acceptance probability where we accept new proposal with $A(x \rightarrow x')$.
%
% One can also think of the image as an image cropped by detection
% bounding box. We synthesize covariance matrix and create NZ-WHO
% template $w(x)$ for particular viewpoint, focal length and CAD model.
% In sum, for new proposal $x'$, we make a NZ-WHO template on the fly 
% We found out that it requires good initialization to converge to
% local minima.

@@

% there are several advantages that was not possible such as
% \textbf{on-the-fly} template generation and making large number of
% templates
\begin{figure}[t]
\centering
    \includegraphics[width=0.7\linewidth]{tuning2} \\ [-5pt]
    \caption{Search space that our fine-tuning stage handles (Sect.~\ref{sec:fine}).}
 \label{fig:moves}
\end{figure}

\paragraph{Initialization.}
Since the objective function is non-convex, we need a good initialization in order to
increase the probability that we find a solution close to the
global optima. We achieve this by first running a discrete,
pre-trained version of our algorithm (i.e., an ensemble of NZ-WHO
templates) in order to get promising candidate 2D bounding boxes and
poses to start from. We then initialize $\theta$ for each of these candidates.
